Preferential Return Behaviors in People's Daily Life: Evidence from semantic enriched geo-located Twitter data

### 2016-08-18 sq_mobility/sq_mobility_twitter.tex
xx
template

\documentclass[a4paper,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{lastpage,fancyhdr,graphicx}
\graphicspath{ {/figure/} }
\usepackage{authblk}

\begin{document}
%\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
\title{Sequential mobility patterns in people's daily life}
\author[1]{Junjun Yin}
\author[2]{Chao Zhang}
\author[1]{Shaowen Wang\thanks{shaowen@illinois.edu}}
\affil[1]{CyberGIS Center for Advanced Digtial and Spatial Studies}
\affil[2]{Department of Computer Science}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}

\renewcommand\Authands{ and }

\maketitle

\section*{\centering Abstract}
Understanding human mobility patterns

@@

\begin{figure}[ht]
	\includegraphics[width=1.0\linewidth]{./figure/firsttime}
	\caption{{\bf The shape of Twitter user mobility in Chicago for year 2014}}
	\label{Fig_shape}
\end{figure}

@@

>>>>

\documentclass[fleqn,10pt]{wlscirep}
\usepackage{graphicx}
\graphicspath{ {/figure/} }

%\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
%\title{Sequential mobility patterns in people's daily life: Evidence from}
\title{Preferential Return Behaviors in People's Daily Life: Evidence from semantic enriched geo-located Twitter data}
\author[1,+]{Junjun  Yin}
\author[1,2,+]{Myeonghun Jeong}
\author[2,3,*]{Zhenhong Du}
\affil[1]{Department of Geography and Geographic Information Science}
\affil[2]{CyberGIS Center for Advanced Digitial and Spatial Studies}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
\affil[3]{Zhejiang University}
\affil[*]{duzhenhong.zju@gmail.com}
\affil[+]{these authors contributed equally to this work}

%\keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. 
\end{abstract}

\begin{document}
\flushbottom
\maketitle

@@

\begin{figure}[ht]
	\includegraphics[width=1.0\linewidth]{./figure/firsttime}
	\caption{{\bf The shape of Twitter user mobility in Chicago for year 2014}}
	\label{first_time_passage}
\end{figure}

@@

\bibliography{ref}
